---
output: html_document
editor_options: 
  chunk_output_type: console
---
This R markdown code was used to compile and analyze FlyTracker x,y data in Wilson et al, 2022.
Author: Emily Petruccelli, Ph.D. (Southern Illinois University Edwardsville) <-- not an R master

```{r}
#Load required libraries
library(readxl)
library(ggplot2)
library(ggrepel)
library(reshape2)
library(RColorBrewer) 
library(plyr) 
library(Rmisc)
library(ggpubr)
library(trajr)
library(tidyr)
library(dplyr)
```

Set the working directory - folder containing list of .xls files to be analyzed + a key.csv file should contain headers that match the following:
Video.name,	Video,	ROI,	Num.flies,	Geno,	TotalFrames,	VideoDuration.min, 35mm

```{r}
file.list <- list.files(pattern='*.xls')
video.key <- read.csv("key.csv")
```

Stack Datasets and use TrajR package to analyze
```{r}
#Make empty variables to fill with all the data 
all_coords<-c() #coordinates from the raw/original .xls files
all_data<-c() #trajr filtered by ROI 35mm, filled in x,y coordinates and new variables/features added

#For loop each .xls
for (i in 1:length(file.list))
{
  #Get video subkey
  subkey<-filter(video.key,Video.name %in% file.list[i])
  
  #Compile data from .xls based on key
  coords<-c()
    for (ii in 1:sum(subkey$Num.flies)+1){
      sub<-read_excel(file.list[i],sheet=ii,range=paste("A1:","B",subkey$TotalFrames[1],sep="")) #only taking A1,B columns (x,y coords)
      coords<-rbind(coords,sub)
    }
  colnames(coords)<-c("x","y") #used to be posx,posy
  
  ## COORDS
  #Label with metadata from Key #New columns
  coords$time<-rep(1:(subkey$TotalFrames[1]-1),subkey$Num.flies)
  coords$time.min<-coords$time/30/60
  geno<-c()
  for (ii in 1:dim(subkey)[1]){ 
    temp<-paste(rep(subkey$Geno[ii],subkey$Num.flies[ii]*dim(sub)[1]))
    geno<-c(geno,temp)
    }
  coords$geno<-geno
  coords$fly<-rep(1:subkey$Num.flies,each=dim(sub)[1])
  coords$vid_ROI<-paste(subkey$Video[1],"_",subkey$ROI[1],sep="")
  coords$fullgenotype<-paste(subkey$fullgenotype)
  coords$cond<-paste(subkey$Condition)
  
  #Make all x,y == 0 be a 'not a number' since this is poor tracking...less than 0.1% of video should be NA
  #coords[, 1:2][coords[, 1:2] == 0] <- NA
  
  #Remove anything outside of 35mm circle ROI
  circ<-matrix(c(max(coords$x,na.rm=T)/2,
              max(coords$y,na.rm=T)/2,
              ###440), nrow=1) #17.5mm radius, 35mm circle circum.== 420pxl... so allow 440 ish?
              subkey$X35mm+20), nrow=1) #17.5mm radius, 35mm circle circum.== 420pxl... so allow 440 ish?
  incirc<-function(x,y){
    new<-((x-circ[1])^2 + (y-circ[2])^2) < circ[3]^2
    return(new)
    }
  coords$circle<-incirc(coords$x,coords$y)
  coords_sub<-filter(coords,circle=="TRUE")
  print(summary(coords$circle))
  
  print("Coords made and labeled")
  print(paste(i))
  
  #Make a trajr, scale to mm, interpolate NA points, calculate derivatives
    trjs<-list() #make a trj for each fly
    for (ii in 1:subkey$Num.flies){
      temp<-na.exclude(filter(coords_sub, fly==ii)) #gets rid of NAs per fly,  dataframes of diff sizes
      trj<-TrajFromCoords(temp,xCol=1,yCol=2,timeCol=3)
      ####trj<-TrajScale(trj, (0.035 / 450), "m") #35mm had a length of 420 pixels, output in m
      trj<-TrajScale(trj, (0.035 / subkey$X35mm), "m") #35mm had a length of image pixels, output in m
      trj<-TrajResampleTime(trj,1) #interpolation, adds missing time units
      #trjsmo<-TrajSmoothSG(trj, p=3, n=31)
      name<-paste(paste(subkey$video.name[1]),'vid',paste(subkey$Video[1]),'fly',ii,sep='_') #name the individual trjs
      trjs[[name]]<-trj #two sets of brackets because trjs is a list of lists
    }
  
    for (ii in 1:length(trjs)){
      derivs<-TrajDerivatives(trjs[[ii]]) #speed and acceleration
      ang<-list(TrajAngles(trjs[[ii]])) #turning angles (radians) of a trajectory, for every time point
      trjs[[ii]]<-c(trjs[[ii]],derivs,ang=ang) #add the trajr data to the butt of trjs
    }
    
    #pull from trjs, put into a dataframe with columns for each feature
    x.trj<-c()  #pxl
    y.trj<-c()  #pxl
    title<-c()
    time<-c()   #frames
    time.min<-c() #min
    fly<-c()
    speed<-c()  #trajr is m/frame
    acc<-c()  #trajr is m/frame^2
    ang<-c()

    for (ii in 1:subkey$Num.flies){
      temp<-trjs[[ii]]
      x.trj<-c(x.trj,temp$x)
      y.trj<-c(y.trj,temp$y)
      title<-c(title,rep(names(trjs)[ii],length(temp$x)))
      time<-c(time,temp$time)
      fly<-c(fly,c(rep(paste(ii),length(temp$x))))
      speed<-c(speed,c(0,temp$speed))  
      acc<-c(acc,c(0,temp$acceleration,0))  
      #intervals <- TrajSpeedIntervals(trj, fasterThan = 2)
      ang<-c(ang,c(0,temp$ang,0))
    }
flytrackerdata<-data.frame(geno=paste(subkey$Geno),vid_ROI=paste(subkey$Video[1],"_",subkey$ROI[1],sep=""),fullgenotype=paste(subkey$fullgenotype),cond=paste(subkey$Condition),title=title,fly=fly,x.trj=x.trj,y.trj=y.trj,time=time,time.min=time/30/60,speed=speed,acc=acc,ang=ang)

  #add cummulative distance traveled
  cumDist<-c() 
  for (j in 1:length(unique(flytrackerdata$fly))){
    temp<-filter(flytrackerdata,fly==j)
    temp2<-cumsum(temp$speed)
    cumDist<-c(cumDist,temp2)
    }
  flytrackerdata$cumDist<-cumDist

  all_coords<-rbind(all_coords,coords) #still includes poor tracking outside of ROI
  all_data<-rbind(all_data,flytrackerdata) #only has filtered data
}    
print("Ready for Dplyr!")
```

Dplyr-ing
```{r}
#calculate x0,y0,vapor,vap columns and make binned time data
anchorit<-function(m){(m - min(m))}
#stretchit<-function(m){(m - min(m))/(max(m)-min(m))}

all_flytrackerdata<-all_data %>% group_by(geno,fullgenotype,cond,vid_ROI,title) %>% 
  mutate(x0=anchorit(x.trj),y0=anchorit(y.trj),uniquefly=paste(geno,title,sep="")) %>%
  mutate(vap=ifelse(time.min<=2,"a","e")) %>%  
  mutate(vapor=ifelse(time.min<=2, "a",ifelse(time.min<=4, "e1",
                  ifelse(time.min<=6, "e2",ifelse(time.min<=8, "e3", "e4"))))) %>%
  mutate(bin=as.numeric(sub("[^,]*,([^]]*)\\]","\\1",cut(time.min,breaks = seq(0,10,1/5)))))


all_binflytrackerdata <- all_flytrackerdata %>% group_by(geno,fullgenotype,cond,vid_ROI,uniquefly,bin) %>%
  summarise(across(c("speed","acc","ang","cumDist","x0","y0"), ~mean(.x,na.rm=T)))


#graphing the all_ variables (takes a bit of time to do)
b<-melt(all_flytrackerdata,id=c("geno","vid_ROI","fullgenotype","cond","title","fly","time","time.min","uniquefly", "vap","vapor","bin"), variable.name = "feat")
bdots<-summarySE(b,measurevar='value',groupvars= ~geno~vid_ROI~fullgenotype~cond~feat,na.rm = TRUE)
bmean<-summarySE(bdots,measurevar='value',groupvars= ~geno~fullgenotype~cond~feat,na.rm = TRUE)
bargraphs <- ggplot(bmean,aes(geno,value,fill=geno))+
  facet_wrap(~feat,scales='free',nrow=2)+
  scale_y_continuous(expand = c(0, 0))+
  #geom_flat_violin(alpha=0.2,position = position_nudge(x = 0.2))+
  geom_col(color="black",width=0.8)+
  geom_errorbar(aes(ymin=value-se,ymax=value+se),width=0.2)+
  geom_jitter(data=bdots, size=0.5,alpha=0.6,width=0.2)+
  theme_classic(base_size = 12)+
  theme(legend.position = "none", axis.text.x = element_blank())


l<-melt(all_binflytrackerdata,id=c("geno","fullgenotype","cond","vid_ROI","uniquefly","bin"), variable.name = "feat")
ldots<-summarySE(l,measurevar='value',groupvars= ~geno~fullgenotype~cond~vid_ROI~bin~feat,na.rm = TRUE)
lmean<-summarySE(ldots,measurevar='value',groupvars= ~geno~fullgenotype~cond~bin~feat,na.rm = TRUE)
linegraphs <- ggplot(lmean,aes(x=bin,y=value,group=geno,color=geno))+  
  geom_rect(xmin=2, xmax=10, ymin=0, ymax=Inf, fill="lightgray",color=NA, alpha=0.5)+
  geom_vline(xintercept = 2,linetype='dashed') + 
  facet_wrap(~feat,scales='free',nrow=2) + 
  geom_ribbon(aes(ymin=value-se,ymax=value+se,fill=as.factor(geno)),color=NA,alpha=.4)+
  geom_line()+ 
  theme_classic(base_size = 12)


ggarrange(bargraphs,linegraphs, ncol=2,widths = c(0.5,1))

```

# somewhat hackish solution to get half violins:
# https://twitter.com/EamonCaddigan/status/646759751242620928
# based mostly on copy/pasting from ggplot2 geom_violin source:
# https://github.com/hadley/ggplot2/blob/master/R/geom-violin.r
# credit goes to David Robinson https://twitter.com/drob
```{r}
"%||%" <- function(a, b) {
        if (!is.null(a)) a else b
}

#' A Flat Violin plot
#'
#' @param mapping See \code{\link[ggplot2]{geom_violin}}
#' @param data See \code{\link[ggplot2]{geom_violin}}
#' @param position See \code{\link[ggplot2]{geom_violin}}
#' @param trim See \code{\link[ggplot2]{geom_violin}}
#' @param scale See \code{\link[ggplot2]{geom_violin}}
#' @param show.legend See \code{\link[ggplot2]{geom_violin}}
#' @param inherit.aes See \code{\link[ggplot2]{geom_violin}}
#' @param ...
#'
#' @export
#'
#' @examples
#' library(ggplot2)
#' ggplot(diamonds, aes(cut, carat)) +
#' geom_flat_violin() +
#' coord_flip()
#'
geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
        ggplot2::layer(
                data = data,
                mapping = mapping,
                stat = stat,
                geom = GeomFlatViolin,
                position = position,
                show.legend = show.legend,
                inherit.aes = inherit.aes,
                params = list(
                        trim = trim,
                        scale = scale,
                        ...
                )
        )
}


GeomFlatViolin <-
        ggplot2::ggproto("GeomFlatViolin", ggplot2::Geom,
                setup_data = function(data, params) {
                        data$width <- data$width %||%
                                params$width %||% (ggplot2::resolution(data$x, FALSE) * 0.9)

                        # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
                        data %>%
                                dplyr::group_by(group) %>%
                                dplyr::mutate(ymin = min(y),
                                       ymax = max(y),
                                       xmin = x,
                                       xmax = x + width / 2)

                },

                draw_group = function(data, panel_scales, coord) {
                        # Find the points for the line to go all the way around
                        data <- transform(data, xminv = x,
                                          xmaxv = x + violinwidth * (xmax - x))

                        # Make sure it's sorted properly to draw the outline
                        newdata <- rbind(plyr::arrange(transform(data, x = xminv), y),
                                         plyr::arrange(transform(data, x = xmaxv), -y))

                        # Close the polygon: set first and last point the same
                        # Needed for coord_polar and such
                        newdata <- rbind(newdata, newdata[1,])

                        ggplot2:::ggname("geom_flat_violin", ggplot2::GeomPolygon$draw_panel(newdata, panel_scales, coord))
                },

                draw_key = ggplot2::draw_key_polygon,

                default_aes = ggplot2::aes(weight = 1, colour = "grey20", fill = "white", size = 0.5,
                                  alpha = NA, linetype = "solid"),

                required_aes = c("x", "y")
        )

```

Diagnostic Heatmaps.. may take a while to run.
```{r}
all_binflytrackerdata %>% 
ggplot(.,aes(x0,y0))+stat_density2d(aes(fill=..density..),geom='raster',contour = F,n=100)+  
  facet_wrap(~geno)+
  scale_fill_distiller(palette='RdYlBu')+
  coord_equal()+
  scale_y_reverse()+
  theme_classic()

all_flytrackerdata %>%
ggplot(.,aes(x0,y0))+stat_density2d(aes(fill=..density../30/60),geom='raster',contour = F,n=100)+
  facet_wrap(~geno)+
  scale_fill_distiller(palette='RdYlBu',limits=c(0,6),breaks=seq(0,6,by=.5))+
  coord_equal()+
  scale_y_reverse()+
  theme_classic()
```



Speed and Air-Baseline adjusting
```{r}
all_flytrackerdata_sub<-all_flytrackerdata
all_binflytrackerdata_sub <- all_flytrackerdata %>% group_by(geno,vid_ROI,fullgenotype,cond,uniquefly,bin,vap,vapor) %>% summarise(across(c("speed"), ~mean(.x,na.rm=T)))



ldots<-summarySE(all_binflytrackerdata_sub,measurevar='speed',groupvars= ~geno~fullgenotype~cond~vid_ROI~bin,na.rm = TRUE)
lmean<-summarySE(ldots,measurevar='speed',groupvars= ~geno~fullgenotype~cond~bin,na.rm = TRUE)
linegraphs <- ggplot(lmean,aes(x=bin,y=speed*1000*30,group=geno,color=geno))+  
  geom_rect(xmin=2, xmax=10, ymin=0, ymax=Inf, fill="lightgray",color=NA, alpha=0.5)+
  geom_vline(xintercept = 2,linetype='dashed') + 
  facet_wrap(~cond,nrow=1) + 
  geom_ribbon(aes(ymin=(speed-se)*1000*30,ymax=(speed+se)*1000*30,fill=as.factor(geno)),color=NA,alpha=.4)+
  geom_line()+ ylab("Speed (mm/sec)")+ 
  theme_classic(base_size = 12)

lbase <- all_binflytrackerdata_sub %>% group_by(geno,vid_ROI,uniquefly) %>% mutate(speed.base=speed - mean(speed[vap=="a"]))
ldots<-summarySE(lbase,measurevar='speed.base',groupvars= ~geno~fullgenotype~cond~vid_ROI~bin,na.rm = TRUE)
lmean<-summarySE(ldots,measurevar='speed.base',groupvars= ~geno~fullgenotype~cond~bin,na.rm = TRUE)
linegraphs.base <- ggplot(lmean,aes(x=bin,y=speed.base*1000*30,group=geno,color=geno))+  
  geom_rect(xmin=2, xmax=10, ymin=0, ymax=Inf, fill="lightblue",color=NA, alpha=0.5)+
  geom_vline(xintercept = 2,linetype='dashed') + geom_hline(yintercept = 0)+
  facet_wrap(~cond,nrow=1) + 
  geom_ribbon(aes(ymin=(speed.base-se)*1000*30,ymax=(speed.base+se)*1000*30,fill=as.factor(geno)),color=NA,alpha=.4)+
  geom_line()+ylab("Speed (mm/sec)")+ 
  theme_classic(base_size = 12)


b <- all_flytrackerdata_sub %>% group_by(geno,fullgenotype,cond,vid_ROI,uniquefly,bin,vap,vapor) %>% filter(cumDist == max(cumDist))
bdots<-summarySE(b,measurevar='cumDist',groupvars= ~geno~vid_ROI~fullgenotype~cond~vap,na.rm = TRUE)
bmean<-summarySE(bdots,measurevar='cumDist',groupvars= ~geno~fullgenotype~cond~vap,na.rm = TRUE)
bargraphs <- ggplot(bmean,aes(geno,cumDist,fill=geno))+
  scale_y_continuous(expand = c(0, 0))+
  geom_col(color="black",width=0.8)+
  geom_flat_violin(data=b,alpha=0.2,position = position_nudge(x = 0.2))+
  geom_errorbar(aes(ymin=cumDist-se,ymax=cumDist+se),width=0.2)+
  geom_jitter(data=bdots, size=0.5,alpha=0.6,width=0.2)+ facet_wrap(~vap)+
  theme_classic(base_size = 12)+ylab("Total Distance Traveled (m)")+
  theme(legend.position = "none", axis.text.x = element_blank())

bbase <- all_flytrackerdata_sub %>% group_by(geno,vid_ROI,uniquefly) %>% mutate(dist.m=cumDist - mean(cumDist[vap=="a"])) #%>% filter(dist.m == max(dist.m))
bdots<-summarySE(bbase,measurevar='dist.m',groupvars= ~geno~vid_ROI~fullgenotype~cond~vap,na.rm = TRUE)
bmean<-summarySE(bdots,measurevar='dist.m',groupvars= ~geno~fullgenotype~cond~vap,na.rm = TRUE)
bargraphs.base <- ggplot(bmean,aes(geno,dist.m,fill=geno))+
  facet_wrap(~vap,nrow=1)+geom_rect(xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, fill="lightblue",color=NA, alpha=0.5)+
  scale_y_continuous(expand = c(0, 0))+
  geom_col(color="black",width=0.8)+
  geom_flat_violin(data=bbase,alpha=0.2,position = position_nudge(x = 0.2))+
  geom_errorbar(aes(ymin=dist.m-se,ymax=dist.m+se),width=0.2)+
  geom_jitter(data=bdots, size=0.5,alpha=0.6,width=0.2)+
  theme_classic(base_size = 12)+ylab("EtOH-Distance Traveled (m)")+
  theme(legend.position = "none", axis.text.x = element_blank())


ggarrange(linegraphs,bargraphs,linegraphs.base,bargraphs.base, nrow=2,ncol=2,widths = c(1,0.5))

```


Histogramical for speed
```{r}
all_flytrackerdata_sub<-all_flytrackerdata
#by cond wrap geno
flies<-summarySE(all_flytrackerdata_sub,measurevar = "speed",groupvars = ~geno~cond~fullgenotype~vid_ROI~uniquefly~vap)
ROIs<-summarySE(flies,measurevar = "speed",groupvars = ~geno~cond~fullgenotype~vid_ROI~vap)
ROIsmean<-summarySE(ROIs,measurevar = "speed",groupvars = ~geno~cond~fullgenotype~vap)

ggplot(flies,aes(x=speed,group=geno,fill=geno))+
  geom_density(alpha=0.3)+
  #geom_jitter(aes(x=speed.avg,y=1,color=geno))+
  geom_rug(aes(color=geno))+
  geom_vline(data = ROIsmean,aes(xintercept = speed,color=geno,linetype=as.factor(cond)))+  
  theme_classic()+theme(legend.position="top")+
  facet_wrap(~vap~fullgenotype)
  #facet_wrap(~vap)


```





###Making figures###
```{r}
all_binflytrackerdata <- all_flytrackerdata %>% group_by(geno,fullgenotype,cond,vid_ROI,uniquefly,bin,vap) %>%
  dplyr::summarise(across(c("speed","acc","ang","cumDist","x0","y0"), ~mean(.x,na.rm=T)))
sub<-subset(all_binflytrackerdata,geno %in% unique(video.key$Geno)[1:6]) 

sub<-subset(all_binflytrackerdata,geno %in% unique(video.key$Geno)[1:3]) 
sub<-subset(all_binflytrackerdata,geno %in% unique(video.key$Geno)[4:6]) 
sub<-subset(all_binflytrackerdata,geno %in% unique(video.key$Geno)[7:9]) 
sub<-subset(all_binflytrackerdata,cond %in% unique(video.key$Condition)[1])
sub<-subset(all_binflytrackerdata,cond %in% unique(video.key$Condition)[2])
sub<-subset(all_binflytrackerdata,cond %in% unique(video.key$Condition)[3])

ROIdots<-summarySE(sub,measurevar="speed",groupvars= ~fullgenotype~cond~geno~vid_ROI~bin)
ROI<-summarySE(ROIdots,measurevar = "speed",groupvars = ~fullgenotype~cond~geno~bin)

line<-ggplot(ROI,aes(x=bin,y=speed*1000*30))+
  #geom_rect(xmin=2, xmax=10, ymin=-Inf, ymax=Inf, fill="thistle1", alpha=0.9,color=NA)+
  geom_rect(xmin=2, xmax=10, ymin=0, ymax=0.5, fill="grey10", alpha=0.9,color=NA)+
  geom_hline(yintercept = 0)+
  geom_ribbon(aes(ymin=(speed-se)*1000*30,ymax=(speed+se)*1000*30,fill=geno),alpha=.6)+
  geom_vline(xintercept = 2,linetype='dashed')+ geom_line(aes(color=geno))+ 
  geom_point(aes(shape=geno,color=geno))+
  scale_x_continuous(name="",breaks=seq(0,10,2)) +
  scale_y_continuous(name="",expand = c(0, 0),limits = c(0,14),breaks=seq(0,14,2))+
  #facet_wrap(~fullgenotype)+   
  #scale_fill_manual(values=c("gray50","red","gray"))+
  #scale_color_manual(values=c("gray50","red","gray"))+
      #scale_fill_manual(values=c("gray","gray50","red"))+
      #scale_color_manual(values=c("gray","gray50","red"))+
        scale_fill_manual(values=c("gray50","gray40","red","red3","gray"))+
        scale_color_manual(values=c("gray50","gray40","red","red3","gray"))+
      #scale_fill_manual(values=c("gray50","gray40","gray10","red","red3","gray","gray70"))+
      #scale_color_manual(values=c("gray50","gray40","gray10","red","red3","gray","gray70"))+
  theme_classic(base_size = 14) + 
      theme(legend.text=element_text(size=10),
            axis.text.x = element_text(color="black"),
            axis.text.y = element_text(color="black"),
            axis.ticks = element_line(color = "black")) #+ 
      theme(legend.position = "none")


edist <- sub %>% group_by(geno,vid_ROI,uniquefly) %>% mutate(dist.m=cumDist - max(cumDist[vap=="a"])) 
ROIdots<-summarySE(edist,measurevar='dist.m',groupvars= ~geno~vid_ROI~fullgenotype~cond~vap,na.rm = TRUE)
ROImean<-summarySE(ROIdots,measurevar='dist.m',groupvars= ~geno~fullgenotype~cond~vap,na.rm = TRUE)

m<-filter(ROImean,vap=="e")
s<-filter(ROIdots,vap=="e")
flydots<-summarySE(edist,measurevar='dist.m',groupvars= ~geno~vid_ROI~uniquefly~fullgenotype~cond~vap,na.rm = TRUE)
b<-filter(flydots,vap=="e")
bar<-ggplot(m,aes(geno,dist.m,fill=geno))+
  #geom_rect(xmin=0, xmax=Inf, ymin=-Inf, ymax=Inf, fill="thistle1", alpha=0.9,color=NA)+
  geom_col(color="black",width=0.4)+
    #scale_fill_manual(values=c("gray50","red","gray"))+
      #scale_fill_manual(values=c("gray","gray50","red"))+
      scale_fill_manual(values=c("gray50","gray40","red","red3","gray"))+
      #scale_fill_manual(values=c("gray50","gray40","red","red3","gray88","gray70","gray"))+
    geom_errorbar(aes(ymin=dist.m-se,ymax=dist.m+se),width=0.2)+
    geom_jitter(data=s,aes(shape=geno),size=2,alpha=0.8,width=0.1)+
  geom_flat_violin(data=b,alpha=0.2,position = position_nudge(x = 0.2))+
    geom_point(data=b, size=0.5,alpha=0.6,position = position_nudge(x = 0.3))+
  #ylab("EtOH-Induced Distance (m)")+ xlab("Genotype")+
  ylab("")+ xlab("")+ facet_wrap(~vap)+
  scale_y_continuous(expand = c(0, 0),limits = c(0,4))+
  #scale_x_discrete(limits=c("Cs_naive_50","Cs_3x24air_50","Cs_3x24etoh_50"))+
  theme_classic(base_size = 14) + 
  theme(legend.position = "none",
        axis.text.y = element_text(color="black"),
        axis.text.x = element_text(color="white"),strip.text.x = element_blank(),
        axis.ticks = element_line(color = "black"))

  
  
#2min
all_binflytrackerdata <- all_flytrackerdata %>% group_by(geno,fullgenotype,cond,vid_ROI,uniquefly,bin,vap,vapor) %>%
  dplyr::summarise(across(c("speed","cumDist"), ~mean(.x,na.rm=T)))

sub<-subset(all_binflytrackerdata,geno %in% unique(video.key$Geno)[1:6]) 
sub<-subset(all_binflytrackerdata,cond %in% unique(video.key$Condition)[2])

edist <- sub %>% group_by(geno,vid_ROI,uniquefly) %>% mutate(dist.m=cumDist - max(cumDist[vap=="a"])) 
edist2 <- edist %>% group_by(geno,vid_ROI,uniquefly,vapor)%>% mutate(dist.t=max(dist.m)-min(dist.m))

ROIdots2<-summarySE(edist2,measurevar='dist.t',groupvars= ~geno~vid_ROI~fullgenotype~cond~vapor,na.rm = TRUE)
ROImean2<-summarySE(ROIdots2,measurevar='dist.t',groupvars= ~geno~fullgenotype~cond~vapor,na.rm = TRUE)

m2<-filter(ROImean2,ROImean2$vapor !="a")
s2<-filter(ROIdots2,ROIdots2$vapor !="a")
flydots2<-summarySE(edist2,measurevar='dist.t',groupvars= ~geno~vid_ROI~uniquefly~fullgenotype~cond~vapor,na.rm = TRUE)
b2<-filter(flydots2,flydots2$vapor !="a")
bar2<-ggplot(m2,aes(geno,dist.t,fill=geno))+
  geom_col(color="black",width=0.4)+
  ylab("")+ xlab("")+ facet_wrap(~vapor, nrow=1)+
    #scale_fill_manual(values=c("gray50","red","gray"))+
      #scale_fill_manual(values=c("gray","gray50","red"))+
      scale_fill_manual(values=c("gray50","gray40","red","red3","gray"))+
      #scale_fill_manual(values=c("gray50","gray40","red","red3","gray88","gray70","gray"))+
    geom_errorbar(aes(ymin=dist.t-se,ymax=dist.t+se),width=0.2)+
    geom_jitter(data=s2,aes(shape=geno),size=2,alpha=0.8,width=0.1)+
  geom_flat_violin(data=b2,alpha=0.2,position = position_nudge(x = 0.2))+
    geom_point(data=b2, size=0.5,alpha=0.6,position = position_nudge(x = 0.3))+
  #ylab("EtOH-Induced Distance (m)")+ xlab("Genotype")+
  scale_y_continuous(expand = c(0, 0),limits = c(0,2))+
  #scale_x_discrete(limits=c("Cs_naive_50","Cs_3x24air_50","Cs_3x24etoh_50"))+
  theme_classic(base_size = 14) #+ 
  theme(legend.position = "none",
        axis.text.y = element_text(color="black"),
        axis.text.x = element_text(color="white"),strip.text.x = element_blank(),
        axis.ticks = element_line(color = "black"))
  
  
  

  
  
ggarrange(line,bar,nrow=1
          ,widths = c(1,0.5)
          )
ggarrange(bar,bar2,nrow=1
          ,widths = c(0.2,1)
          )
ggsave("figure.png", width = 5, height = 3, units = "in",dpi=600)



#STATS
s<-filter(ROIdots,vap=="e")
res.aov<-aov(s$dist.m ~ s$geno)
summary(res.aov)
TukeyHSD(res.aov)

flydots<-summarySE(bbase,measurevar='dist.m',groupvars= ~geno~vid_ROI~uniquefly~fullgenotype~cond~vap,na.rm = TRUE)
b<-filter(flydots,vap=="e")
res.aov<-aov(b$dist.m ~ b$geno)
summary(res.aov)
TukeyHSD(res.aov)

#2min
s2<-filter(ROIdots2,ROIdots2$vapor !="a")
res.aov<-aov(s2$dist.t ~ s2$geno + s2$vapor) #not sure if I should use + or *
summary(res.aov)
TukeyHSD(res.aov) #not sure if I should use Tukey here


```

just bar graphs
```{r}
sub <- all_flytrackerdata %>% group_by(geno,fullgenotype,cond,vid_ROI,uniquefly,bin,vap) %>%
  dplyr::summarise(across(c("speed","acc","ang","cumDist","x0","y0"), ~mean(.x,na.rm=T)))
edist <- sub %>% group_by(geno,vid_ROI,uniquefly) %>% mutate(dist.m=cumDist - max(cumDist[vap=="a"])) %>% filter(cond %in% c("3x24air","3x24etoh")) 
ROIdots<-summarySE(edist,measurevar='dist.m',groupvars= ~geno~vid_ROI~fullgenotype~cond~vap,na.rm = TRUE)
ROImean<-summarySE(ROIdots,measurevar='dist.m',groupvars= ~geno~fullgenotype~cond~vap,na.rm = TRUE)

m<-filter(ROImean,vap=="e")
s<-filter(ROIdots,vap=="e")
flydots<-summarySE(edist,measurevar='dist.m',groupvars= ~geno~vid_ROI~uniquefly~fullgenotype~cond~vap,na.rm = TRUE)
b<-filter(flydots,vap=="e")
bar<-ggplot(m,aes(geno,dist.m,fill=geno))+
  facet_wrap(~cond)+
  geom_rect(xmin=0, xmax=Inf, ymin=-Inf, ymax=Inf, fill="thistle1", alpha=0.9,color=NA)+
  geom_col(color="black",width=0.4)+
    scale_fill_manual(values=rep(c("gray50","red","gray"),each=2))+
    geom_errorbar(aes(ymin=dist.m-se,ymax=dist.m+se),width=0.2)+
    geom_jitter(data=s,aes(shape=geno),size=2,alpha=0.8,width=0.1)+
  geom_flat_violin(data=b,alpha=0.2,position = position_nudge(x = 0.2))+
    geom_point(data=b, size=0.5,alpha=0.6,position = position_nudge(x = 0.3))+
  #ylab("EtOH-Induced Distance (m)")+ xlab("Genotype")+
  ylab("")+ xlab("")+ facet_wrap(~vap)+
  scale_y_continuous(expand = c(0, 0),limits = c(0,4))+
  #scale_x_discrete(limits=c("Cs_naive_50","Cs_3x24air_50","Cs_3x24etoh_50"))+
  theme_classic(base_size = 20) + theme(legend.text=element_text(size=10),axis.text.x = element_text(color="white"),strip.text.x = element_blank())# + theme(legend.position = "none")


setoh<-filter(ROIdots,vap=="e" & cond=="3x24etoh")
sair<-filter(ROIdots,vap=="e"& cond=="3x24air")
amean<-summarySE(sair,measurevar = "dist.m",groupvars = ~geno~fullgenotype)

out<-c()
for (i in 1:length(unique(setoh$fullgenotype))){
  temp<-filter(setoh,fullgenotype %in% unique(setoh$fullgenotype)[i])
  temp2<-filter(amean,fullgenotype %in% unique(setoh$fullgenotype)[i])
  temp$dif<-temp$dist.m - temp2$dist.m
  out<-rbind(out,temp)
}
outmean<-summarySE(out,measurevar='dif',groupvars= ~geno~fullgenotype~cond~vap,na.rm = TRUE)
difbar<-ggplot(outmean,aes(geno,dif,fill=geno))+
  geom_rect(xmin=0, xmax=Inf, ymin=-Inf, ymax=Inf, fill="thistle1", alpha=0.9,color=NA)+
  geom_col(color="black",width=0.4)+
    scale_fill_manual(values=rep(c("gray50","red","gray")))+
    geom_errorbar(aes(ymin=dif-se,ymax=dif+se),width=0.2)+
    geom_jitter(data=out,aes(shape=geno),size=2,alpha=0.8,width=0.1)+
  geom_flat_violin(data=out,alpha=0.2,position = position_nudge(x = 0.2))+
  ylab("")+ xlab("")+
  geom_hline(yintercept=0)+
  #scale_x_discrete(limits=c("Cs_naive_50","Cs_3x24air_50","Cs_3x24etoh_50"))+
  theme_classic(base_size = 20) + theme(legend.text=element_text(size=10),axis.text.x = element_text(color="white"),strip.text.x = element_blank()) + theme(legend.position = "none")


ggarrange(bar,difbar,nrow=1,widths = c(1,0.5))



#STATS
s<-filter(ROIdots,vap=="e")
#test normality
for (i in 1:length(unique(s$geno))){
  temp<-filter(s,geno %in% unique(s$geno)[i])
  print(shapiro.test(temp$dist.m))}
#test homoscedasticity (Bartlett’s test is used to test if variances across samples is equal. It is sensitive to departures from normality. The Levene test is an alternative test that is less sensitive to departures from normality.)
bartlett.test(s$dist.m ~ s$geno)
res.aov<-aov(s$dist.m ~ s$geno*s$cond)
summary(res.aov)
TukeyHSD(res.aov)

flydots<-summarySE(bbase,measurevar='dist.m',groupvars= ~geno~vid_ROI~uniquefly~fullgenotype~cond~vap,na.rm = TRUE)
b<-filter(flydots,vap=="e")
res.aov<-aov(s$dist.m ~ s$cond*s$geno)
summary(res.aov)
TukeyHSD(res.aov)

res.aov<-aov(out$dif~out$geno)
summary(res.aov)
TukeyHSD(res.aov)

```


```{r}
###Tracking Paths
ramp<-colorRampPalette(rev(brewer.pal(11,'Spectral')))
cramp<-ramp(32)
a<-filter(all_flytrackerdata_sub, vid_ROI%in%c("2_1","2_2","2_3","1_1","1_2","1_3") & fly=="4")

ggplot(a, aes(x0,y0)) + 
  #stat_density2d(aes(fill=..density../30/60),geom='raster',contour = F,n=100)+  #get minutes 
  #scale_fill_distiller(palette ='RdYlBu',limits=c(0,6),breaks=seq(0,6,by=.5))+
  geom_path(aes(color=speed*1000*30))+ #get mm/sec
  scale_color_distiller(palette ='RdYlBu',limits=c(0,80),breaks=seq(0,80,by=20))+
  facet_wrap(~vap~geno~cond,nrow=2)+ coord_equal()+ scale_y_reverse()+ theme_classic()

ggplot(a, aes(x0,y0)) + 
  geom_path(aes(color=time.min))+ #get mm/sec
  scale_color_distiller(palette ='Spectral',limits=c(0,10),breaks=seq(0,10,by=0.2))+
  facet_wrap(~geno~vapor~cond,nrow=3)+ coord_equal()+ scale_y_reverse()+ theme_classic()

###Heatmap-ing
b<-all_binflytrackerdata_sub %>% group_by(uniquefly,bin,geno) %>% summarise(speed=mean(speed,na.rm=T),n=n()) %>% arrange(speed)
ggplot(b,aes(bin,uniquefly))+
  geom_tile(aes(fill=speed*1000*30))+
  scale_fill_distiller(palette ='Spectral',limits=c(0,16),breaks=seq(0,16,by=2),na.value = "red")+
  facet_wrap(~geno,scales='free',nrow=2)+
  theme(axis.text.y = element_text(size = 5))
  

sub<-filter(all_binflytrackerdata_sub,fullgenotype %in%  unique(all_binflytrackerdata_sub$fullgenotype)[2])
c<-sub %>% group_by(uniquefly,bin,geno,vid_ROI) %>% summarise(speed=mean(speed,na.rm=T),n=n()) %>% arrange(speed)
fly<-ggplot(c,aes(bin,uniquefly))+
  geom_tile(aes(fill=speed*1000*30))+
  scale_fill_distiller(palette ='Spectral',limits=c(0,16),breaks=seq(0,16,by=2),na.value = "red")+
  facet_wrap(~geno,scales='free',nrow=1)
d<-c %>% group_by(bin,geno) %>% summarise(speed=mean(speed,na.rm=T),n=n())
mean<-ggplot(d,aes(bin,geno))+
  geom_tile(aes(fill=speed*1000*30))+
  scale_fill_distiller(palette ='Spectral',limits=c(0,16),breaks=seq(0,16,by=2),na.value = "red")+
  facet_wrap(~geno,scales='free',nrow=1)

ggarrange(fly,mean,nrow=2,heights = c(1,0.2))
```


